Clean - An Abstract Imperative Programming Language and its Theory

### 2019-09-17 C11-BackEnds/Clean/document/root.tex

\begin{abstract}
Clean  is based on a simple, abstract execution model for an
imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
alternatively, the term ``shallow-style embedding'' could be used. It strives for a type-safe
notation of program-variables, an incremental construction of the typed state-space in order 
to facilitate incremental verification and open-world extensibility to new type definitions 
intertwined with the the program definition.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
is fully \HOL{}-typed and based on an incremental construction based on extensible
records. Direct recursion of operations is supported.

The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately
restrict themselves to the most elementary infrastructure for these tasks. The package is intended to
serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
test-generation technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

>>>>

\begin{abstract}
Clean is based on a simple, abstract execution model for an imperative target language. ``Abstract''
is understood as contrast to ``Concrete Semantics''; alternatively, the term ``shallow-style
embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
construction of typed state-space, facilitating incremental verification approaches, and supports
open-world extensibility of new type definitions while intertwined with the original program
definition.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
is fully \HOL{}-typed, its incremental construction relies on extensible records. Direct recursion
of operations is supported.

The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately restrict
themselves to the most elementary infrastructure for these tasks. The package is intended to serve
as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}
